The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
notes matching kivela syntax

#### Network types and construction (defining layers for the multilayer network)

We generated seasonal multilayer social networks consisting of habitat-specific
monolayers. Each layer was the social association network generated in one of
three habitat types (lichen, open, and forest). For habitat-specific networks,
all GPS relocations were assigned to the corresponding habitat type and
proximity-based social network layers were generated using the R package spatsoc
(Robitaille et al. 2019) in *R version* (R Core Team 2020).

Within each habitat-specific monolayer network, we assumed individuals were
associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
other) were within a given distance of one another. Typically for ungulates and
other gregarious mammals, the ‘chain rule’ is applied for group assignment. For
GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes
buffered by a given distance formed a contiguous buffer for two or more
individuals, even if some individuals within the buffer were not within the
given distance of one another (Robitaille et al. 2019). Group assignment based
on the chain rule has previously been applied to caribou at a distance of 50m
(Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes
represented individuals, intralayer edges represented associations between
individuals in a given habitat type, and interlayer edges represented
connections between the same individuals across contexts.

>>>>

#### Network types and construction (defining layers for the multilayer network)
<!-- specific kivela name, 6 layer multilayer-->

Following [@Kivela_2014]:

* we generated a six layer multilayer social network consisting of two aspects
(season and landcover)
* elementary-layer sets for two seasons (winter and summer) and three landcover
classes (open, forest and lichen).
* This multilayer network is not node-aligned as not all individuals exist on
all layers
* This layer has both ordinal and categorical coupling

Individuals were subset to ensure they had data collected in both seasons

We generated seasonal multilayer social networks consisting of habitat-specific
monolayers. Each layer was the social association network generated in one of
three habitat types (lichen, open, and forest). For habitat-specific networks,
all GPS relocations were assigned to the corresponding habitat type and
proximity-based social network layers were generated using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].

Within each habitat-specific monolayer network, we assumed individuals were
associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
other) were within a given distance of one another. Typically for ungulates and
other gregarious mammals, the ‘chain rule’ is applied for group assignment. For
GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes
buffered by a given distance formed a contiguous buffer for two or more
individuals, even if some individuals within the buffer were not within the
given distance of one another [@Robitaille_2019]. Group assignment based
on the chain rule has previously been applied to caribou at a distance of 50m
[@Peignier_2019; @Lesmerises_2018]. In all networks, nodes
represented individuals, intralayer edges represented associations between
individuals in a given habitat type, and interlayer edges represented
connections between the same individuals across contexts.
